---
title: "p8105_hw1_yw3996"
author: "Yiying Wu"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1
Load the moderndive library:
```{r}
library("moderndive")
```

load the early_january_weather dataset:
```{r}
data("early_january_weather")
```
Here's a short description of the dataset:

* the variables in this dataset includes origin (EWR), year (2013), month (Jan), day (ranges from 1 to 15), hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and the time_hour.  <span style="color: red;">**needs to be clarified**</span> 
* The dataset contains `r nrow(early_january_weather)` records on the weather in early January and `r ncol(early_january_weather)` variables.
* The mean temperature is `r round(mean(early_january_weather$temp),2)`.

Make a scatterplot of temp (y) vs time_hour (x); 
color points using the humid variable (by adding color = ... inside of aes in the ggplot code). 
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point()
```
Here's a description of the plot:

As time went by, the temperature had an increase tendency, the humidity also increased during Jan, 2013. 

Export the scatterplot to the project directory using ggsave.
```{r}
ggsave("p8105_hw1p1_scatterplot.pdf")
```

# Problem 2
The following code creates a data frame (**prb2_df**) comprised of:

* `samp`: a random sample of size 10 from a standard Normal distribution
* `samp_pos`: a logical vector indicating whether elements of the sample are greater than 0
* `char_vec`: a character vector of length 10
* `factor_vec`: a factor vector of length 10, with 3 different factor “levels”
```{r}
prb2_df <- tibble(
  samp = rnorm(10),
  samp_pos = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "medium", "medium", "medium", "high", "high", "high", "high"))
)
```

Take the mean of each variable in the dataframe.
```{r}
mean(pull(prb2_df,samp))
mean(pull(prb2_df,samp_pos))
mean(pull(prb2_df,char_vec))
mean(pull(prb2_df,factor_vec))
```

The numeric and logical variables (`samp` & `samp_pos`) work while the character and factor variables (`char_vec` & `factor_vec`) don't